---
title: "Research"
---

```{r}
#| echo: false
#| warning: false

# ---- config -------------------------------------------------------------
me <- "Yanwan Zhu"

known_types <- c("journal_article", "conference_paper", "preprint",
                 "book_chapter", "dissertation", "under_review",
                 "in_preparation")

# ---- read ---------------------------------------------------------------
pubs <- read.csv("publications.csv", stringsAsFactors = FALSE,
                 na.strings = c("", "NA"))

expected <- c("title", "authors", "year", "publication", "type", "theme",
              "doi", "preprint_url", "github_url", "pdf_url",
              "poster_url", "image")

missing <- setdiff(expected, names(pubs))
for (col in missing) pubs[[col]] <- NA_character_

required <- c("title", "authors", "type", "theme")
if (length(intersect(required, missing))) {
  stop("publications.csv is missing required column(s): ",
       paste(intersect(required, missing), collapse = ", "))
}

pubs$type  <- tolower(trimws(pubs$type))
pubs$theme <- trimws(pubs$theme)

# ---- validate -----------------------------------------------------------
bad <- setdiff(unique(pubs$type), known_types)
if (length(bad)) stop("Unknown type(s): ", paste(bad, collapse = ", "))

no_me <- !grepl(me, pubs$authors, fixed = TRUE)
if (any(no_me)) {
  warning("Name missing from authors for: ",
          paste(pubs$title[no_me], collapse = "; "))
}

.rendered <- character(0)

# ---- helpers ------------------------------------------------------------
fmt_authors <- function(x) {
  a <- trimws(strsplit(x, ";")[[1]])
  a <- ifelse(a == me, paste0("<strong>", a, "</strong>"), a)
  if (length(a) == 1) return(a)
  if (length(a) == 2) return(paste(a, collapse = " & "))
  paste0(paste(a[-length(a)], collapse = ", "), ", & ", a[length(a)])
}

fmt_venue <- function(r) {
  if (is.na(r$publication)) {
    return(switch(r$type,
      under_review   = "Manuscript under review.",
      in_preparation = "In preparation.",
      ""))
  }
  prefix <- if (r$type %in% c("conference_paper", "book_chapter")) "In " else ""
  paste0(prefix, "<em>", r$publication, "</em>.")
}

fmt_links <- function(r) {
  l <- c(
    if (!is.na(r$pdf_url))      sprintf('<a href="%s">Paper</a>', r$pdf_url),
    if (!is.na(r$doi))          sprintf('<a href="https://doi.org/%s">DOI</a>', r$doi),
    if (!is.na(r$preprint_url)) sprintf('<a href="%s">Preprint</a>', r$preprint_url),
    if (!is.na(r$poster_url))   sprintf('<a href="%s">Poster</a>', r$poster_url),
    if (!is.na(r$github_url))   sprintf('<a href="%s">Code</a>', r$github_url)
  )
  if (!length(l)) return("")
  paste0('<div class="pub-links">[', paste(l, collapse = "] ["), ']</div>')
}

# ---- renderer -----------------------------------------------------------
render_pubs <- function(theme) {
  rows <- pubs[pubs$theme == theme, ]
  .rendered <<- c(.rendered, theme)

  if (!nrow(rows)) {
    warning("No publications with theme: ", theme)
    return(invisible())
  }

  yr <- suppressWarnings(as.numeric(rows$year))
  yr[is.na(yr)] <- Inf
  rows <- rows[order(-yr), ]

  for (i in seq_len(nrow(rows))) {
    r <- rows[i, ]
    cat('<div class="pub">\n')
    if (!is.na(r$image)) {
      cat(sprintf('<img class="pub-thumb" src="%s" alt="">\n', r$image))
    }
    cat('<div class="pub-body">\n')
    yr_txt <- if (is.na(r$year)) "" else paste0(" (", r$year, ")")
    cat('<div class="pub-cite">',
        fmt_authors(r$authors), yr_txt, ". ",
        r$title, ". ",
        fmt_venue(r),
        '</div>\n', sep = "")
    cat(fmt_links(r), "\n")
    cat('</div>\n</div>\n\n')
  }
  invisible()
}
```

### Overview

My research interests lie at the intersection of many branches of cognitive science, including but not limited to: developmental psychology, semantics & pragmatics, philosophy of mind, etc. Below is a list of projects I have worked on, organized by topics. 

### Acquisition of possibility concept and language

The main focus of my PhD work has been on children’s concept of possibility — the ability to mark a proposition as being merely possible (like the operator $\Diamond$ in modal logic). I ask: can this logical concept be learned without language, or do they have to be constructed through the process of figuring out what words and phrases mean in a language?

```{r}
#| echo: false
#| output: asis
render_pubs("modal_development")
```

### Language acquisition in understudied populations

When I was an undergrad at Smith College, I worked with Jill de Villiers on a project focusing on Romani-speaking children in Europe. In our paper, in addition to presenting data on Roma children's linguistic knowledge, we argued that studying language acquisition in understudied populations like Roma children is important, highlighting both the scientific merits and the societal implications. 

```{r}
#| echo: false
#| output: asis
render_pubs("language_assessment")
```